Eigenvalues and Eigenvectors of Correlation/Covariance Matrices

### 2015-11-26 papers/segments/CorrelationMatrix.tex
Empirical studies of the correlation matrix.

\input{../../physics_common}
\title{Eigenvalues and Eigenvectors of Correlation/Covariance Matrices}
\author{Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle
\section{Eigenvalues}
% \begin{figure}[htb!]
%   \centering
%   \subfigure[]{
%     \includegraphics[scale=0.3]{Eigenvalues_of_CovarianceMatrix_SP500.pdf}
%   }
%   \subfigure[]{
%     \includegraphics[scale=0.3]{Eigenvalues_of_CorrelationMatrix_SP500.pdf}
%   }
%   \caption{$\log_{10}(\lambda_{(i+1)} / \lambda_{(i)})$ versus $i$}
%   \label{fig:EigenRatio}
% \end{figure}
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5]{Eigenvalues_Cor_n_Cov_Matrix.pdf}  
  \caption{$\log_{10}(\lambda_{(i)})$}
  \label{fig:EigenRatio}
\end{figure}

\section{Eigenvectors}
% \begin{figure}[htb!]
%   \centering
%   \subfigure[]{
%     \includegraphics[scale=0.3]{LargestComponent_of_Eigenvectors_of_CovarianceMatrix_SP500.pdf}
%   }
%   \subfigure[]{
%     \includegraphics[scale=0.3]{LargestComponent_of_Eigenvectors_of_CorrelationMatrix_SP500.pdf}
%   }
%   \caption{$\max_{1 \leq k \leq p} |V_{ki}|$, where $V_{ki}$ is the
%     $k$-th component of the eigenvector associated with the $i$-th
%     largest eigenvalue.}
%   \label{fig:Eigenvector_largest_comp}
% \end{figure}
\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V1_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V1_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}
\bibliographystyle{unsrt}
\bibliography{../thesis/econophysics}
\end{document}

>>>>

\input{../../physics_common}
\title{Eigenvalues and Eigenvectors of Correlation/Covariance Matrices}
\author{Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle
\section{Eigenvalues}
% \begin{figure}[htb!]
%   \centering
%   \subfigure[]{
%     \includegraphics[scale=0.3]{Eigenvalues_of_CovarianceMatrix_SP500.pdf}
%   }
%   \subfigure[]{
%     \includegraphics[scale=0.3]{Eigenvalues_of_CorrelationMatrix_SP500.pdf}
%   }
%   \caption{$\log_{10}(\lambda_{(i+1)} / \lambda_{(i)})$ versus $i$}
%   \label{fig:EigenRatio}
% \end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[$\lambda_{(i)}$]{
    \includegraphics[scale=0.3]{Eigenvalues_Cor_n_Cov_Matrix.pdf}
  }
  \subfigure[$\log_{10}\lambda^{\text{corr}}_{(i)}$
  vs. $\log_{10}\lambda^{\text{cov}}_{(i)}$]{
    \includegraphics[scale=0.3]{Eigenvalues_Cor_vs_Cov_Matrix.pdf}
  }
\end{figure}

% \begin{figure}[htb!]
%   \centering
%   \includegraphics[scale=0.5]{Eigenvalues_Cor_n_Cov_Matrix.pdf}  
%   \caption{$\lambda_{(i)}$}
% \end{figure}

% \begin{figure}[htb!]
%   \centering
%   \includegraphics[scale=0.5]{Eigenvalues_Cor_vs_Cov_Matrix.pdf}  
%   \caption{$\lambda^{\text{corr}}_{(i)}$ vs. $\lambda^{\text{cov}}_{(i)}$}
% \end{figure}

\section{Eigenvectors}
% \begin{figure}[htb!]
%   \centering
%   \subfigure[]{
%     \includegraphics[scale=0.3]{LargestComponent_of_Eigenvectors_of_CovarianceMatrix_SP500.pdf}
%   }
%   \subfigure[]{
%     \includegraphics[scale=0.3]{LargestComponent_of_Eigenvectors_of_CorrelationMatrix_SP500.pdf}
%   }
%   \caption{$\max_{1 \leq k \leq p} |V_{ki}|$, where $V_{ki}$ is the
%     $k$-th component of the eigenvector associated with the $i$-th
%     largest eigenvalue.}
%   \label{fig:Eigenvector_largest_comp}
% \end{figure}
\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V1_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V1_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V2_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V2_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the 2nd largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V3_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V3_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the 3rd largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V4_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V4_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the 4th largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V5_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V5_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the 5th largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Covariance Matrix]{
    \includegraphics[scale=0.3]{V6_CovarianceMatrix.pdf}
  }
  \subfigure[Correlation Matrix]{
    \includegraphics[scale=0.3]{V6_CorrelationMatrix.pdf}
  }
  \caption{Eigenvector corresponding to the 6th largest eigenvalue}
  \label{fig:Eigenvector_largest_comp}
\end{figure}

\bibliographystyle{unsrt}
\bibliography{../thesis/econophysics}
\end{document}
